\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Granit Gashi}}\\
	West New York New Jersey $\cdot$ GranitG1997@gmail.com $\cdot$ (201) 699 9016 $\cdot$ https://www.linkedin.com/in/granitgashi/\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Montclair State University}\hfill New Jersey\\
BS Computer Science \textit{GPA: 3.3} \hfill Sep 2016 - May 2020\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Self Employed}\\
\textit{Mining and Trading crypto currencies} \hfill Nov 2020 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Built a mining rig to mine Ethereum and other crypto currencies such as Dogecoin and Ravencoin
	\item Built multiple computer rigs for personal use and a few associates with a variety of components
	\item Advanced understanding of cryptocurrency exchanges in multiple platforms
	\item Bought and sold different currencies like Dogecoin and Ethereum on tradiing platforms like Robinhood and TrustWallet
	\item Experienced in installing cryptocurrency mining rigs, which includes building racks for the equipment, stacking it, and overall cable mangement
	\item Found new ways to make the mining rigs more effiencent through maintence which involved changing their thermal pads, thermal paste and editing their performance through Hive OS. Which overall increases their HashRate and sometimes even lowers power consumption
\end{itemize}

\textbf{Uncle Paul\textquotesingle{}s Restaurant} \hfill Manhattan, NY\\
\textit{Busser} \hfill Sep 2014 - Sep 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Swept, wiped and cleaned tables before and after individuals arrived.
	\item Interreacted with a lot of people, and showed tremendous respect to each individual.
	\item Ran food from kitchen to table to serve guests.
	\item Refilled drinks, placed water and bread on tables before or after guests arrived
 	\item Experienced in providing a reliable and pleasant experience for all customers.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Java, Javascript, PHP, SQL, React                                                   \\
	Technologies:          & Windows 7/10, Eclipse, JetBrains, GitBash, Git Desktop, Git, macOS, Visual Studios, \\
				& Hive OS	\\
\end{tabular}
\vspace{2mm}

\header{Projects}
{\textbf{Rio Summer Olympics Tickets Platform}} {\sl React, Redux, Javascript} \hfill https://aglasswala.github.io/Summer-Olympics/\#/\\
A platform where three different types of users can register and log in. Regular users can reserve tickets. Administrators can create and update competition events and Athletes another user type can create autograph sessions so that regular users can attend.\\
\vspace*{2mm}
{\textbf{Data Structures and Algorithms}} {\sl Java, Javascript} \hfill https://github.com/GranitG/DataStructuresandAlgorithms\\
Used different Data Structures and Algorithms to complete challenges in LeetCode.com. Able to solve easy problems, medium problems, and some hard problems.\\
\vspace*{2mm}
{\textbf{Organized our own Hackathon}}\\
Montclair State University has never hosted a hackathon before, so the computer club organized our first ever hackathon that had over 130participants. The sponsor list consisted of: Google, Monster and UPS. The hackathon and all of the events were funded by Montclair State University and its sponsors.\\
\vspace*{2mm}

\header{Summary}
\textbf{I am a future software engineer with a broad interest across the stack. I have a particular fondness for learning new data structures, studying software design patterns and creating or working with performant algorithms.}\\

\vspace*{2mm}

\ 
\end{document}